\documentclass{ctexart}
\usepackage{longtable}

\begin{document}
\begin{center}
\begin{longtable}{|l|p{7.8cm}|}

\hline
\multicolumn{2}{|l|}{\textbf{Chapter V. Advice from a Caterpilla}}\\

\hline
languid
&
If you describe someone as languid, you mean that they show little energy or interest and are very slow and casual in their movements.
\\

\hline
chrysalis
&
A chrysalis is a butterfly or moth in the stage between being a larva and an adult. 蛹
\\

\hline
chrysalis
&
A chrysalis is the hard, protective covering that a chrysalis has. 茧
\\


\hline
puff
&
If someone puffs at a cigarette, cigar, or pipe, they smoke it.
\\

\hline
incessant
&
An incessant process or activity is one that continues without stopping.
\\

\hline
somersault
&
If someone or something does a somersault, they turn over completely in the air.
\\

\hline
sage
&
A sage is a person who is regarded as being very wise.
\\

\hline
supple
&
A supple person can move and bend their body very easily.
\\

\hline
supple
&
A supple object or material bends or changes shape easily without cracking or breaking.
\\

\hline
supple
&
If you describe something such as a flavour or a sound as supple, you like it because it is smooth and rich.
\\


\hline
ointment
&
An ointment is a smooth thick substance that is put on sore skin or a wound to help it heal.
\\

\hline
ointment
&
If you describe someone or something as a fly in the ointment, you think they spoil a situation and prevent it being as successful as you had hoped.
\\


\hline
suet
&
Suet is hard animal fat that is used in cooking.
\\


\hline
eel
&
An eel is a long, thin fish that looks like a snake. 鳗鱼
\\

\hline
rear
&
When a horse rears, it moves the front part of its body upwards, so that its front legs are high in the air and it is standing on its back legs.
\\

\hline
morsel
&
A morsel is a very small amount of something, especially a very small piece of food.
\\

\hline
stalk
&
The stalk of a flower, leaf, or fruit is the thin part that joins it to the plant or tree.
\\

\hline
wriggle
&
If you wriggle or wriggle part of your body, you twist and turn with quick movements, for example because you are uncomfortable.
\\

\hline
sulky
&
Someone who is sulky is sulking or is unwilling to enjoy themselves. 生闷气的
\\

\hline
crouch
&
If you are crouching, your legs are bent under you so that you are close to the ground and leaning forward slightly.
\\

\hline
frighten
&
If something frightens the life out of you, frightens the wits out of you, or frightens you out of your wits, it causes you to feel suddenly afraid or gives you a very unpleasant shock.
\\

\hline
\multicolumn{2}{|l|}{\textbf{Chapter VI. Pig and Pepper}}\\

\hline
wag
&
When a dog wags its tail, it repeatedly waves its tail from side to side.
\\

\hline
purr
&
When a cat purrs, it makes a low vibrating sound with its throat because it is contented.
\\

\hline
giddy
&
If you feel giddy, you feel unsteady and think that you are about to fall over, usually because you are not well.
\\

\hline
giddy
&
If you feel giddy with delight or excitement, you feel so happy or excited that you find it hard to think or act normally.
\\

\hline
thatch
&
A thatch or a thatch roof is a roof made from straw or reeds.
\\

\hline
\multicolumn{2}{|l|}{\textbf{Chapter VII A Mad Tea-Party}}\\

\hline
indignant
&
If you are indignant, you are shocked and angry, because you think that something is unjust or unfair. The word shares the same root digus with ignition.
\\

\hline
raven
&
A raven is a large bird with shiny black feathers and a deep harsh call. 渡鸭
\\

\hline
riddle
&
A riddle is a puzzle or joke in which you ask a question that seems to be nonsense but which has a clever or amusing answer.
\\

\hline
meek
&
If you describe a person as meek, you think that they are gentle and quiet, and likely to do what other people say.
\\

\hline
gloomy
&
If people are gloomy, they are unhappy and have no hope.
\\

\hline
contemptuous
&
If you are contemptuous of someone or something, you do not like or respect them at all.
\\

\hline
twinkling
&
a very short time; instant; moment
\\

\hline
pinch
&
If you pinch a part of someone's body, you take a piece of their skin between your thumb and first finger and give it a short squeeze.
\\

\hline
feeble
&
If you describe someone or something as feeble, you mean that they are weak.
\\

\hline
treacle
&
Treacle is a thick, sweet, sticky liquid that is obtained when sugar is processed. It is used in making cakes and puddings.
\\

\hline
jug
&
A jug is a cylindrical container with a handle and is used for holding and pouring liquids.
\\

\hline
shriek
&
a shrill and piercing cry 尖锐刺耳的叫声
\\

\hline
fountain
&
A fountain is an ornamental feature in a pool or lake which consists of a long narrow stream of water that is forced up into the air by a pump.
\\

\hline
\multicolumn{2}{|l|}{\textbf{ CHAPTER IX. The Mock Turtle’s Story}}\\

\hline
vinegar
&
醋
\\

\hline
chamomile
&
甘菊
\\

\hline
barley-sugar
&
麦芽糖
\\

\hline
stingy
&
unwilling to spend or give
\\

\hline
mustard
&
芥末酱
\\

\hline
stamp
&
If you stamp or stamp your foot, you lift your foot and put it down very hard on the ground, for example because you are angry or because your feet are cold.
\\

\hline
gryphon
&
狮身鹰首兽
\\

\hline
ledge
&
A ledge is a piece of rock on the side of a cliff or mountain, which is in the shape of a narrow shelf.
\\

\hline
flapper
&
a person or thing that flaps 鳍
\\

\hline
conger eel
&
海鳗
\\

\hline
crab
&
蟹
\\

\hline
\multicolumn{2}{|l|}{\textbf{Chapter X The Lobster Quadrille}}\\

\hline
punch
&
If you punch someone or something, you hit them hard with your fist.
\\

\hline
salmon
&
A salmon is a large silver-coloured fish. 三文鱼
\\

\hline
jellyfish
&
A jellyfish is a sea creature that has a clear soft body and can sting you. 水母
\\

\hline
somersault
&
If someone or something does a somersault, they turn over completely in the air.
\\

\hline
caper about
&
If you caper about, you run and jump around because you are happy or excited.
\\

\hline
crumb
&
Crumbs are tiny pieces that fall from bread, biscuits, or cake when you cut it or eat it.
\\

\hline
porpoise
&
A porpoise is a sea animal that looks like a dolphin. Porpoises usually swim in groups. 鼠海豚
\\

\hline
sluggard
&
A person who is habitually indolent(lazy).
\\

\hline
pant
&
If you pant, you breathe quickly and loudly with your mouth open, because you have been doing something energetic.
\\

\hline

\end{longtable}
\end{center}
\end{document}
