\documentclass{article}
\usepackage{longtable}

\begin{document}
\begin{center}
\begin{longtable}{|l|p{7.8cm}|}

\hline
\multicolumn{2}{|l|}{\textbf{Chapter 6 Defend the Territory}}
\\

\hline
placid
&
A placid person or animal is calm and does not easily become excited, angry, or upset.
\\

\hline
cantaloupe
&
A cantaloupe is a type of melon.
\\

\hline
snort
&
When people or animals snort, they breathe air noisily out through their noses. People sometimes snort in order to express disapproval or amusement.
\\

\hline
usher
&
If you usher someone somewhere, you show them where they should go, often by going with them.
\\

\hline
recliner
&
A recliner is a type of armchair with a back that can be adjusted to slope at different angles.
\\

\hline
put one's finger on sth
&
If you put your finger on something, for example a reason or problem, you see and identify exactly what it is.
\\

\hline
Young Turk
&
a progressive, revolutionary, or rebellious member of an organization, political party, etc, esp one agitating for radical reform
\\

\hline
Young Turk
&
a member of an abortive reform movement in the Ottoman Empire, originally made up of exiles in W Europe who advocated liberal reforms. The movement fell under the domination of young Turkish army officers of a nationalist bent, who wielded great influence in the government between 1908 and 1918
\\

\hline
stultify
&
If something stultifies you, it makes you feel empty or dull in your mind, because it is so boring.
\\

\hline
esprit de corps
&
Esprit de corps is a feeling of loyalty and pride that is shared by the members of a group who consider themselves to be different from other people in some special way.
\\

\hline
fuss
&
If you fuss, you worry or behave in a nervous, anxious way about unimportant matters or rush around doing unnecessary things.
\\

\hline
huffy
&
Someone who is huffy is obviously annoyed or offended about something.
\\

\hline
petty
&
If you describe someone's behaviour as petty, you mean that they care too much about small, unimportant things and perhaps that they are unnecessarily unkind.
\\

\hline
petty
&
You can use petty to describe things such as problems, rules, or arguments which you think are unimportant or relate to unimportant things.
\\

\hline
innate
&
An innate quality or ability is one which a person is born with.
\\

\hline
turf
&
Turf is short, thick, even grass.
\\

\hline
turf
&
A turf is a small rectangular piece of grass which you lay on the ground in order to make a lawn.
\\

\hline
turf
&
Someone's turf is the area which is most familiar to them or where they feel most confident.
\\

\hline
expenditure
&
Expenditure is the spending of money on something, or the money that is spent on something.
\\

\hline
upshot
&
The upshot of a series of events or discussions is the final result of them, usually a surprising result.
\\


\hline
make do
&
to get along, or manage, with what is available
\\

\hline
morale
&
Morale is the amount of confidence and cheerfulness that a group of people have.
\\

\hline
manger
&
A manger is a low open container which cows, horses, and other animals feed from when indoors.
\\

\hline
malignant
&
A malignant tumour or disease is out of control and likely to cause death.
\\

\hline
malignant
&
If you say that someone is malignant, you think they are cruel and like to cause harm.
\\

\hline
fall on deaf ears
&

\\

\hline
entrench
&
If something such as power, a custom, or an idea is entrenched, it is firmly established, so that it would be difficult to change it.
\\

\hline
clobber
&
If a person or company is clobbered by something, they are very badly affected by it.
\\

\hline
petty cash
&
Petty cash is money that is kept in the office of a company, for making small payments in cash when necessary.
\\

\hline
incarnate
&
If you say that someone is a quality incarnate, you mean that they represent that quality or are typical of it in an extreme form.
\\

\hline
stranglehold
&
To have a stranglehold on something means to have control over it and prevent it from being free or from developing.
\\

\hline
impeccable
&
If you describe something such as someone's behaviour or appearance as impeccable, you are emphasizing that it is perfect and has no faults.
\\

\hline
bash
&
A bash is a party or celebration, especially a large one held by an official organization or attended by famous people.
\\

\hline
foregoing
&
You can refer to what has just been stated or mentioned as the foregoing.
\\

\hline
come to grips with sth
&
If you come to grips with a problem, you consider it seriously, and start taking action to deal with it.
\\

\hline
retaliate
&
If you retaliate when someone harms or annoys you, you do something which harms or annoys them in return.
\\

\hline

\end{longtable}
\end{center}
\end{document}
