\documentclass{article}
\usepackage{longtable}

\begin{document}
\begin{center}
\begin{longtable}{|l|p{7.8cm}|}

\hline
\multicolumn{2}{|l|}{\textbf{Preface}}\\
\hline
accolade
&
If someone is given an accolade, something is done or said about them which shows how much people admire them.
\\

\hline
grapple
&
to try hard to find a solution to a problem
\\

\hline
deluge
&
to send or give sb/sth a large number of things at the same time
\\

\hline
institutionalize
&
To institutionalize something means to establish it as part of a culture, social system, or organization.
\\

\hline
guru
&
a person who is an expert on a particular subject or who is very good at doing sth
\\

\hline
transcend
&
to be or go beyond the usual limits of sth
\\

\hline
charisma
&
the powerful personal quality that some people have to attract and impress other people
\\

\hline
cynical
&
If you are cynical about something, you do not believe that it can be successful or that the people involved are honest.
\\

\hline
the rigour of sth
&
If you refer to the rigours of an activity or job, you mean the difficult, demanding, or unpleasant things that are associated with it.
\\

\hline
academe
&
The academic world of universities is sometimes referred to as academe.
\\

\hline
grandiose
&
If you describe something as grandiose, you mean it is bigger or more elaborate than necessary.
\\

\hline
not care/give a fig
&
If you say that someone doesn't care a fig or doesn't give a fig about something, you are emphasizing that they think it is unimportant or that they are not interested in it.
\\

\hline
platitude
&
A platitude is a statement which is considered meaningless and boring because it has been made many times before in similar situations.
\\

\hline
off-the-cuff
&
An off-the-cuff remark is made without being prepared or thought about in advance.
\\

\hline
distil
&
If a liquid such as whisky or water is distilled, it is heated until it changes into steam or vapour and then cooled until it becomes liquid again. This is usually done in order to make it pure.
\\

\hline
hedonist
&
A hedonist is someone who believes that having pleasure is the most important thing in life.
\\

\hline
impede
&
If you impede someone or something, you make their movement, development, or progress difficult.
\\

\hline
\multicolumn{2}{|l|}{\textbf{Chapter 1 The Question of Happiness}}\\
\hline
alleviate
&
If you alleviate pain, suffering, or an unpleasant condition, you make it less intense or severe.
\\

\hline
exertion
&
energetic activity; effort
\\

\hline
ecstatic
&
If you are ecstatic, you feel very happy and full of excitement.
\\

\hline
retire to
&
If you retire to another room or place, you go there.
\\

\hline
exalted
&
Someone or something that is at an exalted level is at a very high level, especially with regard to rank or importance.
\\

\hline
befuddled
&
confused, muddled, perplexed
\\

\hline
desolate
&
A desolate place is empty of people and lacking in comfort.
\\

\hline
fervent
&
A fervent person has or shows strong feelings about something, and is very sincere and enthusiastic about it.
\\

\hline
predicament
&
If you are in a predicament, you are in an unpleasant situation that is difficult to get out of.
\\

\hline
dire
&
If you describe something as dire, you are emphasizing that it is of very low quality.
\\

&
Dire is used to emphasize how serious or terrible a situation or event is.
\\

\hline
ecstasy (See \textit{ecstatic} above)
&
Ecstasy is a feeling of very great happiness.
\\

\hline
fleeting
&
Fleeting is used to describe something which lasts only for a very short time.
\\

\hline
antecedent
&
An antecedent of something happened or existed before it and was similar to it in some way.
\\

\hline
panacea
&
If you say that something is not a panacea for a particular set of problems, you mean that it will not solve all those problems.
\\

\hline
acute
&
An acute illness is one that becomes severe very quickly but does not last very long.
\\

\hline
acute
&
You can use acute to indicate that an undesirable situation or feeling is very severe or intense.
\\

\hline
spell
&
A spell of a particular type of weather or a particular activity is a short period of time during which this type of weather or activity occurs.
\\

\hline
aspire
&
If you aspire to something such as an important job, you have a strong desire to achieve it.
\\

\hline
despondent
&
If you are despondent, you are very unhappy because you have been experiencing difficulties that you think you will not be able to overcome.
\\

\hline
squander
&
If you squander money, resources, or opportunities, you waste them.
\\

\hline
detract
&
If one thing detracts from another, it makes it seem less good or impressive.
\\

\hline
\multicolumn{2}{|l|}{\textbf{Chapter 3 Happiness Explained}}\\
\hline
insatiable
&
If someone has an insatiable desire for something, they want as much of it as they can possibly get.
\\

\hline
relent
&
If you relent, you allow someone to do something that you had previously refused to allow them to do.
\\

&
If bad weather relents, it improves.
\\

\hline
onslaught of
&
If you refer to an onslaught of something, you mean that there is a large amount of it, often so that it is very difficult to deal with.
\\

\hline
ordain
&
If some authority or power ordains something, they decide that it should happen or be in existence.
\\

&
When someone is ordained, they are made a member of the clergy in a religious ceremony.
\\

\hline
reciprocal
&
A reciprocal action or agreement involves two people or groups who do the same thing to each other or agree to help each another in a similar way.
\\

\hline
ploy
&
A ploy is a way of behaving that someone plans carefully and secretly in order to gain an advantage for themselves.
\\

\hline
tumor
&
A tumor is a mass of diseased or abnormal cells that has grown in a person's or animal's body.
\\

\hline
lobe
&
The lobe of your ear is the soft, fleshy part at the bottom.
\\

&
If you describe someone as apathetic, you are criticizing them because they do not seem to be interested in or enthusiastic about doing anything.
\\

\hline
apathetic
&
If you describe someone as apathetic, you are criticizing them because they do not seem to be interested in or enthusiastic about doing anything.
\\

\hline
ramification
&
The ramifications of a decision, plan, or event are all its consequences and effects, especially ones which are not obvious at first.
\\

\hline
propel
&
To propel something in a particular direction means to cause it to move in that direction.
\\

\hline
tribulation
&
You can refer to the suffering or difficulty that you experience in a particular situation as tribulations.
\\

\hline
psychotic
&
Someone who is psychotic has a type of severe mental illness.
\\

\hline
euphoric
&
If you are euphoric, you feel intense happiness and excitement.
\\

\hline
delusion
&
Delusion is the state of believing things that are not true.
\\

\hline
circumvent
&
If someone circumvents a rule or restriction, they avoid having to obey the rule or restriction, in a clever and perhaps dishonest way.
\\

\hline
tantamount
&
If you say that one thing is tantamount to a second, more serious thing, you are emphasizing how bad, unacceptable, or unfortunate the first thing is by comparing it to the second.
\\

\hline
endow
&
If you endow something with a particular feature or quality, you provide it with that feature or quality.
\\

\hline
tangible
&
If something is tangible, it is clear enough or definite enough to be easily seen, felt, or noticed.
\\

\hline
imbue
&
If someone or something is imbued with an idea, feeling, or quality, they become filled with it.
\\

\hline
overarching
&
You use overarching to indicate that you are talking about something that includes or affects everything or everyone.
\\

\hline
graze
&
When animals graze or are grazed, they eat the grass or other plants that are growing in a particular place. You can also say that a field is grazed by animals.
\\

\hline
pasture
&
Pasture is land with grass growing on it for farm animals to eat.
\\

\hline
Sanskrit
&
Sanskrit is an ancient language which used to be spoken in India and is now used only in religious writings and ceremonies.
\\

\hline
accolade
&
If someone is given an accolade, something is done or said about them which shows how much people admire them.
\\

\hline
fervor
&
Fervor for something is a very strong feeling for or belief in it.
\\

\hline
draw on
&
If you gratify your own or another person's desire, you do what is necessary to please yourself or them.
\\

\hline
gratify
&
If you gratify your own or another person's desire, you do what is necessary to please yourself or them.
\\

\hline
dispense
&
When a chemist dispenses medicine, he or she prepares it, and gives or sells it to the patient or customer.
\\

\hline
synergistic
&
acting together
\\

\hline
motif
&
A motif is a theme or idea that is frequently repeated throughout a piece of literature or music.
\\

\hline
exigency
&
The exigencies of a situation or a job are the demands or difficulties that you have to deal with as part of it.
\\

\hline
\multicolumn{2}{|l|}{\textbf{Chapter 4 The Ultimate Currency}}\\
\hline
rampant
&
If you describe something bad, such as a crime or disease, as rampant, you mean that it is very common and is increasing in an uncontrolled way.
\\

\hline
destitution
&
Destitution is the state of having no money or possessions.
\\

\hline
on the verge of
&
If you are on the verge of something, you are going to do it very soon or it is likely to happen or begin very soon.
\\

\hline
autistic
&
If someone is autistic, they have a developmental disorder that can cause them to have difficulty in communicating with and responding to other people.
\\

\hline
deficit
&
A deficit is the amount by which something is less than what is required or expected, especially the amount by which the total money received is less than the total money spent.
\\

\hline
ramification
&
The ramifications of a decision, plan, or event are all its consequences and effects, especially ones which are not obvious at first.
\\

\hline
caviar
&
Caviar is the salted eggs of a fish called a sturgeon. (尤指鲟鱼的鱼子制作的)鱼子酱
\\

\hline
longitudinal
&
of or in length
\\

\hline
illusory
&
If you describe something as illusory, you mean that although it seems true or possible, it is in fact false or impossible.
\\

\hline
hoard
&
If you hoard things such as food or money, you save or store them, often in secret, because they are valuable or important to you.
\\

\hline
pay heed
&
If you take heed of what someone says or if you pay heed to them, you pay attention to them and consider carefully what they say.
\\

\hline
rever
&
If you revere someone or something, you respect and admire them greatly.
\\

\hline
solvent
&
If a person or a company is solvent, they have enough money to pay all their debts.
\\

\hline
stride
&
A stride is a long step which you take when you are walking or running.
\\

\hline
ethnic
&
Ethnic means connected with or relating to different racial or cultural groups of people.
\\

\hline
listless
&
Someone who is listless has no energy or enthusiasm.
\\

\hline
dejection
&
Dejection is a feeling of sadness that you get, for example, when you have just been disappointed by something.
\\

\hline
melancholy
&
Melancholy is an intense feeling of sadness which lasts for a long time and which strongly affects your behaviour and attitudes.
\\

\hline
lament
&
If you lament something, you express your sadness, regret, or disappointment about it.
\\

\hline
fanantical
&
If you describe someone as fanatical, you disapprove of them because you consider their behaviour or opinions to be very extreme.
\\

\hline
charismatic
&
A charismatic person attracts, influences, and inspires people by their personal qualities.
\\

\hline
\multicolumn{2}{|l|}{\textbf{Chapter 5 Setting Goals}}\\
\hline
hestitancy
&
hesitation or indecision; doubt
\\

\hline
providence
&
Providence is God, or a force which is believed by some people to arrange the things that happen to us.
\\

\hline
paraplegic
&
A paraplegic is someone who cannot move the lower half of their body, for example because of an injury to their spine.
\\

\hline
ambivalence
&
the simultaneous existence of two opposed and conflicting attitudes, emotions, etc
\\

\hline
accolade
&
If someone is given an accolade, something is done or said about them which shows how much people admire them.
\\

\hline
meandering
&
If you meander somewhere, you move slowly and not in a straight line.
\\

\hline
siren
&
A siren is a warning device which makes a long, loud noise. Most fire engines, ambulances, and police cars have sirens.
\\

&
Some people refer to a woman as a siren when they think that she is attractive to men but dangerous in some way.
\\

\hline
articulate
&
When you articulate your ideas or feelings, you express them clearly in words.
\\

\hline
at the mercy of
&
If one person or thing is at the mercy of another, the first person or thing is in a situation where they cannot prevent themselves being harmed or affected by the second.
\\

\hline
\multicolumn{2}{|l|}{\textbf{Chapter 6 Happiness in Education}}
\\
\hline
climax
&
The climax of something is the most exciting or important moment in it, usually near the end.
\\

\hline
ethos
&
An ethos is the set of ideas and attitudes that is associated with a particular group of people or a particular type of activity.
\\

\hline
stifle
&
If someone stifles something you consider to be a good thing, they prevent it from continuing.
\\

\hline
antithetical
&
Something that is antithetical to something else is the opposite of it and is unable to exist with it.
\\

\hline
conducive
&
If one thing is conducive to another thing, it makes the other thing likely to happen.
\\

\hline
deprivation
&
If you suffer deprivation, you do not have or are prevented from having something that you want or need.
\\

\hline
oxymoron
&
If you describe a phrase as an oxymoron, you mean that what it refers to combines two opposite qualities or ideas and therefore seems impossible.
\\

\hline
affluenza
&
the guilt or lack of motivation experienced by people who have made or inherited large amounts of money
\\

\hline
curb
&
If you curb something, you control it and keep it within limits.
\\

\hline
predicament
&
If you are in a predicament, you are in an unpleasant situation that is difficult to get out of.
\\

\hline
vantage
&
a state, position, or opportunity affording superiority or advantage
\\

\hline
aloofness
&
the quality or state of being distant, detached, or uninvolved
\\

\hline
quintessential
&
Quintessential means representing a perfect or typical example of something.
\\

\hline
banish
&
If someone or something is banished from a place or area of activity, they are sent away from it and prevented from entering it.
\\

\hline
banish
&
If you banish something unpleasant, you get rid of it.
\\

\hline
squander
&
If you squander money, resources, or opportunities, you waste them.
\\

\hline
elusive
&
Something or someone that is elusive is difficult to find, describe, remember, or achieve.
\\

\hline
revelry
&
Revelry is people enjoying themselves in a noisy way, often while they are drunk.
\\

\hline
delude
&
To delude someone into thinking something means to make them believe what is not true.
\\

\hline
infatuation
&
If you have an infatuation for a person or thing, you have strong feelings of love or passion for them which make you unable to think clearly or sensibly about them.
\\

\hline
fatuous
&
If you describe a person, action, or remark as fatuous, you think that they are extremely silly, showing a lack of intelligence or thought.
\\

\hline
conspire
&
If two or more people or groups conspire to do something illegal or harmful, they make a secret agreement to do it.
\\

\hline
frivolous
&
If you describe someone as frivolous, you mean they behave in a silly or light-hearted way, rather than being serious and sensible.
\\

\hline
mesmerize
&
If you are mesmerized by something, you are so interested in it or so attracted to it that you cannot think about anything else.
\\

\hline
innate
&
An innate quality or ability is one which a person is born with.
\\

\hline

\end{longtable}
\end{center}
\end{document}
